```{r christmas.constants}
height.vid <- 9/16
width.vid  <- 16/9

```{r christmas.1}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15)
)
```

```{r christmas.2}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15)
)
```

```{r christmas.3}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15),
    asp=1
)
```

```{r christmas.4}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15),
    asp=1,
    xlab='',
    ylab='',
    main=''
)
```

```{r christmas.5}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15),
    asp=1,
    xlab='',
    ylab='',
    main='',
    type='n'
)
```

```{r christmas.final}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15),
    asp=1,
    xlab='',
    ylab='',
    main='',
    type='n',
    axes=F
)
```

```{r christmas.with.axes}
plot(
    x=-2+c(1,80),
    y=-15+c(-15,height.vid*80-15),
    xlim=-2+c(1,80),
    ylim=-15+c(-15,height.vid*80-15),
    asp=1,
    xlab='',
    ylab='',
    main='',
    type='n',
    axes=F
)
axis(1)
axis(2)
```
